\section{Summary}

Carbon emissions, air pollution, and unemployment challenge environmental sustainability,   Unemployment and economic downturns 

Exelon Generation annouced planned premautre closures of two nuclear plants, .
Byron and Dresden. Both plants, within the PJM interconnection \comment{double check}. 

The extent to which Decarbonization goals at the state level will be undermined by these closures.  
Clean energy goals will not be reached if these plants prematurely retire. Additionally, the eocnomic value provided by these plants to the surrounding community will be lost. 



CEJA/Path to 100/Something Else/Clean Jobs Coalition/Climate union jobs act
The Byron and Dresden communities are 
 This report  closures, planned for Fall 2021.  We expect to reveal regionally relevant findings consistent with the February 2021 National Academy of Sciences, Engineering, and Medicine report, “Accelerating Decarbonization of the U.S. Energy System”, which determined unequivocally that US decarbonization will require keeping existing nuclear plants open \cite{national_accelerating_2021}.

significant amounts of air pollution during operation. Within the area governed by the PJM electrical
interconnection, three currently operating nuclear
plants have submitted plans for closure. In this report, we investigate the air pollution implications of
the potential closure of these plants, as well as the
implications of the potential decommissioning of
other nuclear plants in PJM. We assume that if a nuclear plant is decommissioned, its historical generation will be replaced by other generators currently
in PJM. We model the air pollution caused by generating this replacement electricity, then use standard
epidemiological and economic relationships to estimate health impacts and monetized damages from
this additional air pollution. We find that if the
three nuclear plants in PJM that are currently scheduled to close (providing 3\% of total PJM generation)
are replaced with generation with the averag


Exelon Generation plans to close Byron and Dresden Nuclear Plants in the fall of 
2021 closure of these plants is driven by concern over their
economic competitiveness in the current electricity market. However, nuclear power plants
provide benefits that are not often captured in the revenue they generate, such as a steady
supply of carbon-free electricity, a large tax base to the state and local community, and
hundreds of permanent, well-paying jobs.

Eleven (11) carbon free nuclear power reactors at 6 sites produce the majority of 
electricity in Illinois and critically underpin its clean energy future. We 
propose to quantitatively demonstrate the role nuclear energy must play in 
maximizing job creation, minimizing cost, and meeting Illinois’ carbon goals 
through 2050. We propose to conduct a 50-year techno-economic optimization of 
the Illinois energy system and to analyze scenarios with and without the 
at-risk plants to compare and contrast the economic and carbon implications of 
these energy futures. 



If Dresden and Byron close:
Illinois will see a 30\% hit to carbon-free electricity
wind and solar will not be able to make up this  gap
we will have to start using natural gas \& coal in their place
Thousands of people’s jobs will be at risk 
Including current University of Illinois students
Communities will lose a huge source of funding for them 
Nuclear power plants in Illinois pay a lot of property taxes that fund schools and communities
Exelon has a culture of volunteering and supporting the community
Intern Service Projects
Quad Cities Interns Raised \$34,100 for River Bend Food Bank and the Quad Cities Disaster Recovery Fund

4 other at-risk plants
Here are some contributions made by those 4 plants  
\$3.5 billion to state GDP
28,000 in-state jobs (direct & secondary)
Maintain \$149 million in annual state tax revenue 
Avoid 45 million metric tons of CO2 emissions each year
Illinois consumers and businesses would pay about \$483 million 
more annually for electricity without these four plants

In Illinois, we enjoy a remarkably clean energy mix thanks to our nuclear power plants. The six modestly-sized plants produce 90\% of the clean electricity in Illinois and over half of our total electricity  generation. They run reliably day and night, unaffected by weather. They also require a remarkably small footprint, and their waste is tiny in volume, carefully managed and presents no risks to the public, now or in the future. These nuclear plants are the crucial ingredient in any low-carbon industrial future for the state, and are threatened with shutdown decades before any need to consider decommissioning for technical reasons. 
Luckily, Illinois’ nuclear plants are among the best in the world, and there is no reason they shouldn’t continue to run for decades to come. Nuclear plants of similar design and vintage around the world are seeing the lives of their reactors extended to 80 years, with no limitation in sight. Further, with proper maintenance and part replacement, these plants can continue to operate like new even further beyond that. 
If these nuclear plants are forced to close, and they will without action from the state or the electricity market, they will be replaced by natural gas, not solar and wind. This has been the result in Vermont, California, Massachusetts and just last year in New York with the closure of Indian Point. Not only would this be bad for emissions goals, but also for consumers who will pay \$480 million per year in higher rates, according to a recent report from Brattle. If these nuclear plants close, citizens of Illinois will be forced to pay more money to support the operation of fossil fuel plants in Indiana and Ohio that don't protect the environment or pay for their own carbon emissions. 
The premature closure of the state’s nuclear plants will especially impact the towns and communities that rely on them. Nuclear plants are economic engines that provide permanent, high-wage, high-skilled jobs for generations. And for every 100 nuclear power plant jobs, 66 more jobs are created in local communities. Replacing in-state nuclear generation with out-of-state natural gas will result in a net job loss for Illinois.  



I’ll need to go into listen only mode for the remainder of the call. The update from UIUC is busy. The UIUC ANS student section has been calling, writing emails, and mailing letters to legislators. Each legislator's staff has been contacted by at least one student. Many attended the webinar earlier this week (which many of you were so involved in!). The sustainability institute at Illinois, in collaboration with the NPRE department, will be putting on a "Critical Conversation" event on the role of nuclear in a clean energy future. There will be a very famous climate scientist who has just agreed to give the keynote. That event will be May 5, with the keynote happening at noon. I will share more information through this group when the registration link is live. 
